### 2015-09-29 untitled.tex
edited untitled.tex

This report will explain

\section{Mismatche of Self-Suspending Tasks and Deferrable Tasks}

>>>>

\section{Schedulable Self-Suspending Tasks but Unschedulable Period Enforcer}

Let's consider a system with $2$ tasks. Let $C_1 = 2$ and $T_1=D_1=10$ (without self-suspension). Let $C_{2,1} = 1, S_{2,1} = 6, C_{2,2}=1, T_2=D_2=11$. Suppose that we use the rate-monotonic priority assignment, i.e., $\tau_1$ has higher priority than $\tau_2$. This task system is feasible without any enforcement since at most one computation segment of a job of $\tau_2$ can be affected by $\tau_1$. The worst-case response time of task $\tau_2$ is hence $10$.
